---
title: "Homework 3"
output: html_document
date: '2022-04-16'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidymodels)
library(ISLR) # For the Smarket data set
library(ISLR2) # For the Bikeshare data set
library(discrim)
library(poissonreg)
library(corrr)
library(klaR) # for naive bayes
tidymodels_prefer()
```

## Question 1

```{r}
titanic <- read.csv("~/Downloads/homework-3/data/titanic.csv")
titanic$survived <- factor(titanic$survived,levels=c('Yes', 'No'))
titanic$pclass <- factor(titanic$pclass)

set.seed(2424)

titanic_split <- initial_split(titanic, prop = 0.80,
                                strata = survived)
titanic_train <- training(titanic_split) 
titanic_test <- testing(titanic_split)
```
It is a good idea to use stratified sampling for this data since each subgroup of the given population is adequately represented within the whole sample population.


## Question 2
Using the training data set, explore/describe the distribution of the outcome variable survived.

```{r}
titanic_train %>% 
  ggplot(aes(x = survived)) +
  geom_bar()
```

We can see from the graph that there are much more people who did not survive versus those who did survive. 


## Question 3

```{r}
cor_titanic_train <- titanic_train %>%
  select(-c(survived, pclass, name, sex, ticket, cabin, embarked)) %>%
  correlate()
rplot(cor_titanic_train)
```

From the correlation matrix, we can see that sib_sp and age are negatively related, parch and age are negatively related, parch and sib_sp are positively related, fare and sib_sp are positively related, and fare and parch are positively related.


## Question 4
Using the training data, create a recipe predicting the outcome variable survived. Include the following predictors: ticket class, sex, age, number of siblings or spouses aboard, number of parents or children aboard, and passenger fare.

Recall that there were missing values for age. To deal with this, add an imputation step using step_impute_linear(). Next, use step_dummy() to dummy encode categorical predictors. Finally, include interactions between:

Sex and passenger fare, and
Age and passenger fare.
You’ll need to investigate the tidymodels documentation to find the appropriate step functions to use.
```{r}
titanic_recipe <- 
  recipe(survived ~ ., data = titanic_train%>%select(survived, sex, age, sib_sp, pclass, fare, parch)) %>% 
  step_impute_linear(age) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact(terms = ~ starts_with("sex"):fare + age:fare) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors())
```


## Question 5
```{r}
log_reg <- logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification")

log_wkflow <- workflow() %>% 
  add_model(log_reg) %>% 
  add_recipe(titanic_recipe)

log_fit <- fit(log_wkflow, titanic_train)

predict(log_fit, new_data = titanic_train, type = "prob")

augment(log_fit, new_data = titanic_train) %>%
  conf_mat(truth = survived, estimate = .pred_class)

log_reg_acc <- augment(log_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
log_reg_acc
```

## Question 6
```{r}
lda_mod <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

lda_wkflow <- workflow() %>% 
  add_model(lda_mod) %>% 
  add_recipe(titanic_recipe)

lda_fit <- fit(lda_wkflow, titanic_train)

predict(lda_fit, new_data = titanic_train, type = "prob")

augment(lda_fit, new_data = titanic_train) %>%
  conf_mat(truth = survived, estimate = .pred_class) 

lda_acc <- augment(lda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
lda_acc
```


## Question 7
```{r}
qda_mod <- discrim_quad() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

qda_wkflow <- workflow() %>% 
  add_model(qda_mod) %>% 
  add_recipe(titanic_recipe)

qda_fit <- fit(qda_wkflow, titanic_train)

predict(qda_fit, new_data = titanic_train, type = "prob")

augment(qda_fit, new_data = titanic_train) %>%
  conf_mat(truth = survived, estimate = .pred_class) 

qda_acc <- augment(qda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
qda_acc
```


## Question 8
```{r}
nb_mod <- naive_Bayes() %>% 
  set_mode("classification") %>% 
  set_engine("klaR") %>% 
  set_args(usekernel = FALSE) 

nb_wkflow <- workflow() %>% 
  add_model(nb_mod) %>% 
  add_recipe(titanic_recipe)

nb_fit <- fit(nb_wkflow, titanic_train)

predict(nb_fit, new_data = titanic_train, type = "prob")

augment(nb_fit, new_data = titanic_train) %>%
  conf_mat(truth = survived, estimate = .pred_class) 

nb_acc <- augment(nb_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
nb_acc
```

